\section*{Publications}

\href{\cvADSLink}{ADS search \faLink}% -- \href{\cvORCIDLink}{ORCiD profile \faLink}


\subsection*{First author}

\begin{etaremune}
    \item \publication
        {Emily L. Hunt, Tristan Cantat-Gaudin, Friedrich Anders \emph{et al.}}
        {2025}
        {The completeness of the open cluster census towards the Galactic anticentre}
        [A\&A, accepted]
        [https://ui.adsabs.harvard.edu/abs/2025arXiv250618708H/abstract]
        %[]
    \item \publication
        {Emily L. Hunt and Sabine Reffert}
        {2024}
        {Improving the open cluster census. III. Using cluster masses, radii, and dynamics to create a cleaned open cluster catalogue}
        [A\&A, 686, A42]
        [https://ui.adsabs.harvard.edu/abs/2024arXiv240305143H/abstract]
        [70]
    \item \publication
        {Emily L. Hunt and Sabine Reffert}
        {2023}
        {Improving the open cluster census. II. An all-sky cluster catalogue with Gaia DR3}
        [A\&A, 673, A114]
        [https://ui.adsabs.harvard.edu/abs/2023A\%26A...673A.114H]
        [193]
    \item \publication
        {Emily L. Hunt and Sabine Reffert}
        {2021}
        {Improving the open cluster census. I. Comparison of clustering algorithms applied to Gaia DR2 data}
        [A\&A, 646, A104]
        [https://ui.adsabs.harvard.edu/abs/2021A\%26A...646A.104H]
        [101]https://ui.adsabs.harvard.edu/abs/2023A\%26A...673A.114H
\end{etaremune}


\subsection*{Co-author}

\begin{etaremune}
    \item \publication 
        {Richard I. Anderson and Emily L. Hunt}
        {2025}
        {A birds-eye view of stellar evolution through populations of variable stars in Galactic open clusters}
        [A\&A, submitted]
        % []
        % []
    \item \publication 
        {Sebastian Ratzenböck, João Alves, Emily L. Hunt \emph{et. al}}
        {2025}
        {Toward the fabric of the Milky Way: I. The density of disk streams from a local 250\textsuperscript{3} pc\textsuperscript{3} volume}
        [A\&A, 694, A307]
        [https://ui.adsabs.harvard.edu/abs/2025A\%26A...694A.307R/abstract]
        % []
    \item \publication
        {Dane Spaeth, Sabine Reffert, Emily L. Hunt \emph{et. al}}
        {2024}
        {Non-radial oscillations mimicking a brown dwarf orbiting the cluster giant NGC 4349 No. 127}
        [A\&A, 689, A91]
        [https://ui.adsabs.harvard.edu/abs/2024A\%26A...689A..91S/abstract]
        [2]
    \item \publication
        {Cameren Swiggum \emph{et. al} (incl. Emily L. Hunt)}
        {2024}
        {Most nearby young star clusters formed in three massive complexes }
        [Nature, 661, 8019, p.49-53]
        [https://ui.adsabs.harvard.edu/abs/2024Natur.631...49S/abstract]
        [11]
\end{etaremune}
